|

### 2025-01-31 doc/paper.qmd
paper final

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true  # Enables List of Figures
    lot: true  # Enables List of Tables
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
$$
BHR_{\text{annual}} = (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1, \quad \text{where } R_t \text{ is the daily return and } T \text{ is the total trading days in a year.}
$$

Next, perform cross-sectional regression for each firm/year - the main objective of @ball_how_2008's research:
$$
R_{\text{annual}} = \alpha_0 + \alpha_1 R_{\text{event}_1} + \alpha_2 R_{\text{event}_2} + \alpha_3 R_{\text{event}_3} + \alpha_4 R_{\text{event}_4} + \epsilon_i
$$

@@

## Results {#sec-results3}
Comparing the replication results with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies. The original figure shows a general upward trend in abnormal  R^2 , peaking in the early 2000s, whereas the replicated figure captures greater volatility in the later years (2010–2023). Additionally, Ball’s figure suggests a smoother long-term dynamic, while the replication exhibits more pronounced fluctuations, particularly post-2010. Panel B in replicated figure exhibits higher volatility and larger coefficient magnitudes, suggesting increased earnings informativeness post-2006, while Ball’s original figure has more stable and lower-magnitude coefficients.

>>>>

bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true  # Enables List of Figures
    lot: false  # Disables List of Tables
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true 
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}  # Added this line to ensure the first paragraph is indented for better readability
  - \usepackage[margin=1in]{geometry}
---

@@

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
$$
\begin{aligned}
BHR_{\text{event}} &= (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1
\\
\text{where } R_t & \text{ is the daily return and } T \text{ is the total trading days in a year.}
\end{aligned}
$$

Next, perform cross-sectional regression for each firm/year - the main objective of @ball_how_2008's research:
$$
R_i(\text{annual}) = a_0 + a_1 R_i(\text{window1}) + a_2 R_i(\text{window2}) + a_3 R_i(\text{window3}) + a_4 R_i(\text{window4}) + \varepsilon_i
$$

@@

## Results {#sec-results3}
Comparing the replication results with those from @ball_how_2008 (see @fig-fig1_original) reveals both similarities and discrepancies. The original figure shows a general upward trend in abnormal  R² , peaking in the early 2000s, whereas the replicated figure captures greater volatility in the later years (2010–2023). Additionally, Ball’s figure suggests a smoother long-term dynamic, while the replication exhibits more pronounced fluctuations, particularly post-2010. Panel B in replicated figure exhibits higher volatility and larger coefficient magnitudes, suggesting increased earnings informativeness post-2006, while Ball’s original figure has more stable and lower-magnitude coefficients.
